\documentclass{scrartcl}
\input{includes/shared}

\begin{document}
\subject{Proposal of OOP-Project SS17---Biemann}
\title{Application}
\subtitle{Group 12 (Medical Hospice Application)}
\author{Marino, Dominik\\Stergiou, Charalambos\\ Hamiani, Samir}%Use format lastname, surname in separated lines for each participant
\date{\today}
\maketitle
%\tableofcontents % Use this only if you have more than two pages

%%%%%%%%%% Let's start %%%%%%%%%%

% The following is an example structure you can use. Feel free to adapt this to your needs.
% Remark: Sectioning makes only sense if you have enough content/text. Avoid sections with less than a few lines of text.
\section{Idea}
Our Idea is an application for a hospice to reduce the health risk for dementia person. Today it is so, that people get older and older and the risk to get dementia is higher. During the progress of dementia, the brain loss the ability to recognise that their are thirsty and risk the dehydration. The application should recording the lifestyle of the patients and calculate the water requirements and observe them to take the medicine and to drink water. 

\section{Implementing the Requirements}
To reach the goal to protect the patient from suffering there are two groups in a hospice. The nurses and the doctors. Every one has a specific work in the hospice. So our requirements for the hospice application are:
\begin{itemize}
    \item At fist there is a login interface that decide in which group you apply. 
       \begin{itemize}
     \item The doctor can only prescribe the medicines because he is the supervisor of the application.
     \item If you are a nurse you can add new patients and protocol the condition.
   \end{itemize}
   \item In the doctors GUI he can list all patients, prescribe medicine and do diagnoses
        \item In the nurse GUI manage patient data
    \item The nurse and the doctor can insert, update and delete the database.
\end{itemize}

\section{Details}
The doctor should have an overview of the patient condition and the completed work of the nurses. For the nurses it should be easy to document her task, fulfill the orders from the doctor and document the patient behavior.
\section{Division of work}

We will have an appointment once a week, to work together on the project. We've planned to design a project plan and decide than which part will be done each week. We will work together and help each other by implementation to reach our goal.
In our weekly appointment we will define the goal, split it to the members and document the process of the members work. 

\printbibliography

% Do not forget your signatures
\ThreeSignatures{Dominik Marino}{Charalambos Stergiou}{Samir Hamiani} % For four signatures use it twice
%\ThreeSignatures{Martin Mustermann}{John Doe}{Lucky Luke}

\end{document}